%-------------------------
% Resume in Latex
% Author : Rishi Yang
% Based off of: https://github.com/sb2nov/resume and https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% Indented project heading
\newcommand{\resumeIndentedProjectHeading}[2]{%
    \hspace*{0.12in}
    \begin{tabular*}{0.95\textwidth}{l@{\extracolsep{\fill}}r}
      • \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Rishi Tikare Yang} \\ \vspace{1pt}
    \small 505-377-0420 $|$ \href{mailto:rishtyang@gmail.com}{\underline{rishtyang@gmail.com}} $|$ Berkeley, CA $|$
    \href{https://linkedin.com/in/rishi-yang/}{\underline{linkedin.com/in/rishi-yang}} $|$
    \href{https://github.com/rishikiram}{\underline{github.com/rishikiram}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {Bachelor of Arts in Computer Science — GPA: 3.8}{May. 2024}
      \resumeItemListStart
        \resumeItem{(Math) -  Machine Learning, Probability and Random Processes, Optimization, Discrete Math}
        \resumeItem{(Software) - Databases, Algorithms,  Data Structures, Computer Architectures and Programs}
        \resumeItem{(Technologies) - Robotics, Photovoltaic Devices, Energy Markets in the Clean Transition}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
  % EnviTrace
    \resumeSubheading
      {EnviTrace LLC}{Oct. 2024 -- Nov. 2025}
      {Software Developer}{Santa Fe, NM}
      \resumeItemListStart
        \resumeItem{Processed and visualized geospatial data (primarily subsurface data), developed ML analyses, studied geoscience.}
        \resumeItem{Developed a web application for geospatial AI analyses. Used the Next.js framework to integrate data processing pipelines, ML models (trained CNNs, NMF, and XGBoost)  and visualization tools (3D/2D plots \& maps with Plotly.js \& Kepler), using Julia backend and an API.}
        \resumeItem{Curated a combined dataset of geophysical, geochemical, and hydrological data for machine learning analysis. Researched, scraped, and cleaned public data using GIS softwares and custom tools. Executed unsupervised ML techniques (NMF, K-Means) to cluster data. Developed interpolation techniques to fit data to a regular grid.}
        \resumeItem{Built a seismic event relational database with PostgreSQL. Developed ETL scripts and pipelines for data normalization and cleaning, and conducted data validation. Executed event detection algorithms (FAST similarity search) on raw data seismic data and ingested new events.}
        % \resumeItem{Conducted data analysis correlating geophysical measurements and geologic hydrogen. Established a relationship between gravity anomaly and failed rifts, and no relationship with magnetic anomaly. Applied correlation measures, chi-square tests of independence, mutual information measures, and regressions to assess variable relationships. }
      \resumeItemListEnd

      
% -----------Multiple Positions Heading-----------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 - Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
  %  \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Sandia National Laboratories}{Jun. 2023 -- Aug. 2023}
      {Summer Undergraduate Laboratory Internship (SULI)}{Albuquerque, NM}
      \resumeItemListStart
        \resumeItem{Researched using an optical computer to extract features from material microstructure data for phase classification}
        \resumeItem{Developed model of the optical computer Python with GPU optimizations using PyTorch. Executed statistical analysis of outputs using scikit-learn, and visualized results with matplotlib. }% TODO
        % \resumeItem{Developed networking software to remotely run optical experiments in the laser lab.} 
        \resumeItem{Developed figures, presented results, gave an oral presentation, and wrote a scientific-paper style report}
    \resumeItemListEnd

    \resumeSubheading
      {Berkeley Engineers and Mentors}{Aug. 2020 -- May 2024}
      {Outreach Head, Site Leader, Mentor}{Berkeley, CA}
      \resumeItemListStart
        \resumeItem{Lead the Outreach committee responsible for organizing 15 volunteer/socials events and building club community.}
        \resumeItem{Lead group of 4-5 college students to teach weekly science lessons at local schools for 3 semesters.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{BirdCLEF+2026 Kaggle} $|$ \emph{PyTorch, Classification Model, Sound Event Detection}}
          {Current Project}
          \resumeItemListStart
            \resumeItem{Designed and developed a Sound Event Detection (SED) model combining convolutional and autoregressive neural networks. Built using PyTorch and trained with a GPU. Currently iterating the model architecture and training strategy.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Robotic Arm Sorting} $|$ \emph{ROS2, Robotic Control, Computer Vision, K-Means Clustering}}
          {Fall 2023}
          \resumeItemListStart
            \resumeItem{Developed software to adaptively model the environment from a moving camera using fiducial markers for computer vision. Implemented unsupervised object segmentation with k-means clustering, and an inverse kinematic controller to pick and place blocks with a UR5. Robotic system was designed to test environment representations.}
            \resumeItem{Worked with Kaylene Stocking, a PhD candidate researching object-centric representations and robotic interaction.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Julia, SQL, Typescript, C, Java}\\
     \textbf{Tools \& Libraries}{: PyTorch, Flux.jl, Next.js, React, PlotlyJS, PostgreSQL, Scikit-learn, QGIS}\\ 
     \textbf{Interpersonal Skills}{: Leadership, Teamwork, Technical Communication. Fluent in English and Spanish}\\
     \textbf{Interests}{: Soccer, Tennis, Outdoors Activities, Cooking, Origami, Ceramics, Learning Languages}
    }}
  \end{itemize}

\end{document}